Labor Markets and Technological Change:

### 2022-08-17 Presentations/YESconference.tex

\begin{frame}{Job Setting Variables}
\begin{enumerate}
    \item Fraction of patients seen in office 
                \vspace{3mm}
    \begin{itemize}
        \item Broken up by whether the physician already worked in an office pre-EHR
    \end{itemize}
                \vspace{3mm}
    \item Indicator for working in office or not
\end{enumerate}
\end{frame}

@@

\begin{frame}{Results: Frac of Patients in Office (Prior Work in Office)}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_frac_prior_all.pdf}
\end{figure}
$\rightarrow$ Decrease fraction of patients
\end{frame}

\begin{frame}{Results: Frac of Patients in Office (No Prior Work in Office)}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_frac_noprior_all.pdf}
\end{figure}
$\rightarrow$ Increase fraction of patients
\end{frame}

\begin{frame}{Indicator for working in office}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_office_all.pdf}
\end{figure}
$\rightarrow$ 4.6\% increase relative to the mean\\
$\rightarrow$ Driven by young physicians
\end{frame}

@@

\begin{frame}{Productivity Variables}
    \begin{enumerate}
        \item Patient Count
        \vspace{6mm}
        \item Claims per patient
    \end{enumerate}
\end{frame}

@@

\begin{frame}{Patient Count}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_patients_all.pdf}
\end{figure}
$\rightarrow$ 5-10\% increase relative to the mean\\
$\rightarrow$ Driven by demand? 
\end{frame}

@@

\begin{frame}{Claims per Patient}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_claimperpatient_all.pdf}
\end{figure}
$\rightarrow$ Downward trend
\end{frame}

@@

\begin{frame}{Summary}
\begin{itemize}
    \item Evidence that physicians are changing their behavior because of this new technology, specifically through retirement or job switching
                \vspace{3mm}
    \item Little evidence of work setting changes
                \vspace{3mm}
    \item For physicians who endure through the implementation of the technology, number of patients goes up but not conclusive evidence that claims per patient goes down
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Job Setting Variables}
\begin{enumerate}
    \item Indicator for working in office or not
                    \vspace{3mm}
    \item Indicator for whether the physician changed zip code
\end{enumerate}
\end{frame}

@@

\begin{frame}{Results: Indicator for Working in Office}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_office_all.pdf}
\end{figure}
$\rightarrow$ 4.6\% increase relative to the mean\\
$\rightarrow$ Driven by young physicians
\end{frame}

\begin{frame}{Results: Indicator for Changing Zip Codes}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_zip_all.pdf}
\end{figure}
$\rightarrow$ Something happening in relative year -3, may be a pre-trend
\end{frame}

\begin{frame}{Results: Indicator for Changing Zip Codes}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_zip_ages.pdf}
\end{figure}
$\rightarrow$ .043 ppt increase in likelihood of retiring for younger physicians (36\%)
$\rightarrow$ This effect is persistent
\end{frame}

@@

\begin{frame}{Productivity Variables}
    \begin{enumerate}
        \item Patient count
        \vspace{6mm}
        \item Claims per patient
    \end{enumerate}
\end{frame}

@@

\begin{frame}{Results: Patient Count}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_patients_all.pdf}
\end{figure}
$\rightarrow$ 5-10\% increase relative to the mean\\
$\rightarrow$ Driven by demand? 
\end{frame}

@@

\begin{frame}{Results: Claims per Patient}
\begin{figure}[ht]
\centering
\includegraphics[scale=.35]{Objects/Presentation_claimperpatient_all.pdf}
\end{figure}
$\rightarrow$ Downward trend
\end{frame}

@@

\begin{frame}{Summary}
\textcolor{red}{Downside}: evidence that physicians are changing their behavior because of this new technology\\
                \vspace{6mm}
\textcolor{teal}{Potential upside}: For physicians who endure through the implementation of the technology, number of patients goes up and claims per patient goes down

\end{frame}
